On the performance of the MAC model

### 2018-10-31 2018_nips_vigil/appendix.tex
Description of content of appendix

@@

@@

>>>>

\begin{enumerate}
\item Some description (with link to the paper) about the datasets. Maybe we can "import" material from main paper, making it lighter...
\item Table with attributes/feature combinations of CLEVR/CoGenT-A/CoGenT-B
\item Some exemplary pictures?
\end{enumerate}

@@

We think that in the main paper we should leave:
\begin{itemize}
\item first row - MAC - train on CLEVR, test on CLEVR 
\item all rows regaring S-MAC
\end{itemize}

When we will fill the whole table we will copy the results in here.

@@

\begin{itemize}
\item one with color failure -- that the attention is pointing at the right object, whereas the answer is improper because he never saw this combination
\item one with shape failure -- similarly	
\end{itemize}
Pictures with some description
